Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-19 vesicle_code/docs/adhesion/revisions/summary_of_changes.tex

\item In Section IV: Adhesion of two vesicles in a planar extensional flow, we conducted new simulation to elucidate the interaction between two vesicles in a planar extensional flow. These results are summarized in Figure 6.

@@

\item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the oscillation of the vesicle doublet and how the oscillation frequency depends on 
the shear rate, separation distance, and Hamaker constant. These results are summarized in Figure 13(b). We also did some analysis to compare the double oscillation with the Jeffery orbit of a rigid ellipse in shear flow.

@@

\item In Section V: Adhesion of two vesicles in a shear flow, we corrected the calculation of the intrinsic viscosity and the new results are summarized in Figure 15.

>>>>

\item In Section IV: Adhesion of two vesicles in a planar extensional
  flow, we conducted new simulations to elucidate the interaction
    between two vesicles in a planar extensional flow. These results are
    summarized in Figure 6.

@@

\item In Section V: Adhesion of two vesicles in a shear flow, we conducted more simulations to examine the oscillation of the vesicle doublet and how the oscillation frequency depends on 
the shear rate, separation distance, and Hamaker constant. These results are summarized in Figure 13(b).

\item In Section V: We did some analysis to compare the double
  oscillation with the Jeffery orbit of a rigid ellipse in shear flow.
    These results are summarized in Table I.

@@

\item In Section V: Adhesion of two vesicles in a shear flow, we
  corrected the calculation of the intrinsic viscosity and the new
    results are summarized in Figure 15.  We also discussed the effect
    of the separation distance on the intrinsic viscosity.

\item In Section VI: We have modified the conclusions to include a
  discussion of our new results.
